Progress Report for CSS 586 Project: \\ Music Generation Using Deep Learning

### 2021-05-04 papers/progress/jack/progress-jack.tex
Update to Jack's report

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{mel_spec.png}
  \caption{Mel spectrogram of a 10 second sound segment from the dataset. The color represents the amplitude in dB.}
  \label{spectrogram}
\end{figure}

@@

\section{Progress}
Initially, a lot of time was spent on understanding different representation of the input data. We also learned 
about the basics of sequence models such as RNN, GRU, and LSTM. Because the dataset is large and cannot be loaded into 
the memory at once, we are working on a data pipeline that processes the raw audio files as described in the Section 
Data Processing and presents training examples one by one to a model.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{mel_spec.png}
  \caption{Mel spectrogram of a 10 second sound segment from the dataset. The color represents the magnitude in dB.}
  \label{spectrogram}
\end{figure}

@@

\section{Progress}
Initially, a lot of time was spent on understanding different representations of the input data and on selecting a
viable representation that could be used to train a model. The key is that we can also reliably convert this
representation back to a sound wave. A number of representations are available: the raw waveform, the complex numbers,
the FFT of the waveform, the spectrogram, the mel spectrogram, and the mel frequency ceptral coefficients (MFCC). We decided
to use the mel spectrogram because it is a compressed version of the sound wave, which could be reliably convert back to 
audio. We also learned about the basics of sequence models such as RNN, GRU, and LSTM. Because the dataset is large and 
cannot be loaded into the memory at once, we are working on a data pipeline that processes the raw audio files and presents training examples 
one by one to a model. This pipeline will slice the input files into short audio fragments to be used as input. Then,
it will process the fragments as described in Section Data Processing. The resulting spectrograms will be save
to disk. The training code will load them into memory as needed to train the model.
